---
title: "Testing Functions"
format: html
editor: visual
---

```{r}
library(testthat)
library(devtools)
library(remotes)
```

## Making a function

Given data frame with numeric column, calc means across columns and return the max and min mean values

```{r}
mean_range <- function(df) {
  col_means <- apply(X = df, MARGIN = 2, FUN = mean, na.rm = TRUE)
  col_mean_max <- max(col_means)
  col_mean_min <- min(col_means)
  return(c(col_mean_min, col_mean_max))
}
```

```{r}
mean_range(mtcars)

mean_range(faithful)
```

This function should always return two numeric values in a matrix.

## Unit-testing the function

```{r}
expect_length(mean_range(mtcars), 2)
```

-   nothing returned, so the function is working as expected

```{r}
expect_type(mean_range(mtcars), "character")
```

-   it's expecting to return a numeric value and not a character

```{r}
expect_true(mean_range(mtcars)[1] <= mean_range(mtcars)[2])
```

-   we expect the minimum value returned to be less than or equal to the maximum value returned
